---
title: "Data 550 Project 2"
author: "Sophia Bulcock, Ryan Koenig"
date: "29/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, echo=FALSE, include=FALSE}
#load the libraries
library(ggplot2)
library(GGally)
library(grid)
library(gridExtra)
library(tidyverse)
```
# Palmer Penguins EDA

## Description of Dataset





```{r setup_penguins, messages=FALSE, error=FALSE, include=FALSE}
library(palmerpenguins)
data(package = 'palmerpenguins')
```

## Exploration of Dataset


```{r explore}

#exploring the first 5 rows of raw data
head(penguins_raw)

#exploring the last 5 rows of raw data
tail(penguins_raw)

#counting rows
nrow(penguins_raw)

#summary statistics of the numerical columns
summary(Filter(is.numeric, penguins_raw))
```
Exploring NA values

```{r}
#counting the of missing/NA values per column 
colSums(is.na(penguins_raw))
```

## Initial Observations

1. 

2. 

3. 

4. 


## Wrangling


```{r wrangling}


```


```{r q1_wrangling}

```
For looking at Isotope levels:
```{r q2_wrangling}

```

For looking at the physical comparisons:
```{r q4_wrangling}

```

## Research Questions




## Data Analysis & Visualizations


```{r sex_demo, fig.align='center', echo=FALSE}
 
```


```{r mass_sex_species, fig.align='center', echo=FALSE}

```




```{r corr, fig.align='center', echo=FALSE, warning=FALSE}

```



```{r example_of_facet, fig.height=7, fig.width=8, fig.align='center', echo=FALSE}

  
  
```


```{r Isotope, fig.width=10, fig.height=4, fig.align='center', echo=FALSE}

```



```{r Isotope2,fig.width=10, fig.height=4, fig.align='center', echo=FALSE}

```

It also appears that there is a slight correlation of the proportion of isotope found in the penguins blood and which island they live on.


## Summary





## Conclusion



## Follow-up Questions

1. 


2. 

